The Evolution of Phenotypically Invariant Genetic Networks

### 2017-06-07 handnotes.tex
added to attic
added figure F1

@@

>>>>

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.5\textwidth]{A2_A2-1_F2s}
        \caption{F2s from $A(2)$ and $A(2.1)$.}
      \end{figure}

@@

      \jss{Discussion guidelines:
        \begin{itemize}
        \item Why is this important/useful?
        \item What are the assumptions and shortcomings of the research?
        \item Compare to other studies in the literature. 
        \item Future directions. 
        \item Wild speculations?
        \item Conclusion and overall impact. 
      \end{itemize}}

  The complexity of biological systems has limited our understanding of their function and evolution. Above we outline an approach, a first step, towards untangling this complexity in reference to function and evolution. This methodology borrows successfully applied tools from engineering and aims to synthesize these with the concepts and tools of molecular and evolutionary biology. Theoretical models in evolution and population genetics often lack the molecular details of physiology or of the genotype-phenotype map. Here, we offer a tractable and simple model which includes these missing features. Further, we provide, in clear mathematical language, a description of phenomena hitherto only discussed verbally and conceptualy (phenogenetic drift, developmental systems drift, biological degeneracy, \emph{etc.}). The tractability and relative simplicity of this exposition enables the interested biologist to work out by hand, if desired, the dynamics of a genetic system, as well as perturbations to the system -- an attribute not likely to be found in less tractable models and simulations.
